Objective-First Nanophotonic Design Plan

### 2012-08-29 plan/plan.tex
Updated plan.

\section{Capabilities of our software}
We have implemented various 
    \emph{optimization paradigms} and \emph{structure parameterizations}
    which a user can arbitrarily combine in order to 
    design nanophotonic devices.

@@

\subsection{Definition of physics residual}
The physics residual corresponds to the electromagnetic wave equation
    \E  {wave equation in E}
        {(\curl \mu^{-1} \curl - \omega^2 \epsilon) E = -i \omega J}
    which is described as $A_i(z)x_i - b_i(z)$ via
    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$,
    \I  $\epsilon \in z$,
    \I  $E \to x_i$, and
    \I  $-i \omega J \to b_i(z)$. \EI

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the following relationship,
    \E  {bi-affine}
        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
    which will prove to be very useful.

@@

\section{Properties of the problem}
\subsection{nonconvexity}
\subsection{optimality condition}

>>>>

\section{Capabilities of our software}\label{capabilities of our software}
We have implemented various 
    \emph{optimization paradigms} and \emph{structure parameterizations}
    which a user can arbitrarily combine in order to 
    design nanophotonic devices.

@@

\subsection{Definition of physics residual}
The physics residual corresponds to the electromagnetic wave equation
    \E  {wave equation in E}
        {(\curl \mu^{-1} \curl - \omega^2 \epsilon) E = -i \omega J}
    which is described as $A_i(z)x_i - b_i(z)$ via
    \BI $\curl \mu^{-1} \curl - \omega^2 \epsilon \to A_i(z)$,
    \I  $\epsilon \to z$,
    \I  $E \to x_i$, and
    \I  $-i \omega J \to b_i(z)$. \EI

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the following relationship,
    \E  {bi-affine property}
        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
    which will prove to be very useful.

@@

\section{Properties of the problem}
We now examine the general mathematical properties 
    of the stated problem \eq{rigorous problem statement}.

\subsection{Convexity analysis}
% \subsubsection{Joint non-convexity}
First we note that, as presented, 
    \eq{rigorous problem statement} is non-convex 
    in the variables $x_i$ and $z$. % Ref boyd book
Not only are the physics residuals $A_i(z)x_i - b_i(z)$ non-convex,
    but the field design objective, in that it implements the 
    $ \alpha_{ij} \le |c_{ij}\T x_i| $ constraint, is non-convex as well.

That our problem is non-convex means that it is fundamentally hard to solve
    because of the existence of multiple local minima.
Additionally, even if we were to arrive at the global maxima,
    we would not have a straightforward way to verify global optimality.
Lastly, fast convergence even to local minima may be difficult
    because methods such as Newton's method
    can not be directly applied to non-convex problems.

% \subsubsection{Separable convexity}
That said, \eq{rigorous problem statement} is \emph{separably convex} 
    in $x_i$ and $z$ if we ignore the non-convexity
    in the field design objectives, $f_i(x_i)$, and
    assume that the structure design objective, $g(z)$, is convex as well.
This is given because of the bi-affine property
    of the physics residual, as shown in \eq{bi-affine property}.

The separably convex, or \emph{bi-convex}, properties of our problem
    open the door for the use of alternating direction algorithms,
    and specifically the alternating directions 
    methods of multipliers (ADMM), % Ref. 
    for the implementation of a global optimization paradigm,
    as referred to in section \ref{capabilities of our software}.
Of course, in this context we do not use the term ``global'' rigorously,
    but only to differentiate it from strategies that rely
    purely on local information.

Lastly, since our problem is not bi-convex 
    in the case of non-convex field or structure design objectives,
    simple extensions to alternating direction algorithms are employed.

\subsection{optimality condition}
